### 2021-07-19 README.Rmd
update readme (remove note about PAT)

A GitHub [personal access token](https://github.com/settings/tokens) must be in the environment variable `GITHUB_PAT` or supplied as a string to `auth_token`. See `?remotes::install_github`.

>>>>

<!-- A GitHub [personal access token](https://github.com/settings/tokens) must be in the environment variable `GITHUB_PAT` or supplied as a string to `auth_token`. See `?remotes::install_github`.  -->
